---
title: "Exercise 2 - Practice"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Welcome to the Star Wars Universe!

## Recap: Last Week's `Star Wars`Homework

1\. How many droids are there?

```{r eval=FALSE, include=TRUE}
starwars %>%
   filter(species == 'Droid') %>%
   summarise(n())
```

2\. What is the home world of Han Solo?

```{r eval=FALSE, include=TRUE}
starwars %>%
   select(name, homeworld) %>%
   filter(name == 'Han Solo')
```

3\. How many characters are there per species? Sort by ascending count.

```{r eval=FALSE, include=TRUE}
starwars %>%
    group_by(species) %>%
    summarise(count = n()) %>%
    arrange(desc(count))
```

4\. Change the height from ´cm´ to ´m´.

```{r eval=FALSE, include=TRUE}
starwars %>%
   mutate(height = height / 100)
```

5\. Filter out all characters that have missing values (´NA`) for their mass. How many are left?

```{r eval=FALSE, include=TRUE}
starwars %>%
   select(name, mass) %>%
   na.omit()
```

## Further `Star Wars` Tasks - Breakout Rooms

1\. Find all characters with yellow eyes.

2\. Remove all Gungans. How many characters are left?

3\. What is the average mass of all droids?

4\. Calculate the BMI for all humans (\`mass / ((height / 100) ^ 2)\`)

5\. Which character has the longest name?

6\. What is the earliest birth year for each species (\`birth_year\` is measured in BBY = Before Battle of Yavin, so high values = earlier)

7\. What are the most populated planets?

8\. What is the average height of all female humans?

9\. Which planet has the most droids? 

10\. Which is the most prevalent eye color on each planet?

11\. How many unique eye colors are there?

## Dummify Variables

1.  Install the `tidyfst` package: `install.packages("tidyfst")`.
    Afterwards, load it with `library(tidyfst)`.

2.  Download the `starwars_dd.csv` file from GitHub. For ease of use:
    place it in the folder which is shown in the `Files` section of
    RStudio.

The following code was used to generate the `starwars_dd.csv` file, in
case you are curious (this is not part of this exercise).

``` r
> library(tidyverse)
> starwars %>% 
+       unnest(cols=films,keep_empty=TRUE) %>% 
+       unnest(cols=vehicles, keep_empty=TRUE) %>% 
+       unnest(cols=starships, keep_empty=TRUE) %>%
+       write.csv('./starwars_dd.csv')
```

3.  Import `starwars_dd.csv` into a variable named `starwars_dd`. The
    contents are different from the tidyverse-internal `starwars`
    dataset and simplify the next steps for you.
    
``` r
> read_csv('./starwars_dd.csv') -> starwars_dd
```

4.  Import the `tidyfst` package. Then generate dummies for all films
    and store them in the variable `starwars_films_dd`. Inspect them in
    RStudio (using the `View` function) afterwards. You may use the
    [:book:
    `dummy_dt`](https://www.rdocumentation.org/packages/tidyfst/versions/0.9.9/topics/dummy_dt)
    function from `tidyfst`. Make sure to exclude rows which hold no
    additional information, we are focusing on the different films here
    (Hint: Each character has multiple rows for each film, vehicle and
    starship)
    
``` r
> library(tidyfst)
> starwars_dd %>% 
+       distinct(name, films, .keep_all=TRUE) %>% 
+       dummy_dt(films) ->
+       starwars_films_dd
> starwars_films_dd <- as_tibble(starwars_films_dd)
> View(starwars_films_dd)
```

5.  How many characters starred in `A New Hope`?

``` r
> starwars_films_dd %>% 
+       filter(`films_A New Hope` == 1) %>% 
+       summarise(name, `films_A New Hope`)
# A tibble: 18 x 2
name                  `films_A New Hope`
<chr>                              <dbl>
1 Beru Whitesun lars                     1
2 Biggs Darklighter                      1
3 C-3PO                                  1
4 Chewbacca                              1
5 Darth Vader                            1
6 Greedo                                 1
7 Han Solo                               1
8 Jabba Desilijic Tiure                  1
9 Jek Tono Porkins                       1
10 Leia Organa                            1
11 Luke Skywalker                         1
12 Obi-Wan Kenobi                         1
13 Owen Lars                              1
14 R2-D2                                  1
15 R5-D4                                  1
16 Raymus Antilles                        1
17 Wedge Antilles                         1
18 Wilhuff Tarkin                         1 
```

6.  Which of those characters are female?

## May the Functions Be With You
#### Mastering Function Definition and Manipulation in R with the Star Wars Universe
Complete the following tasks using the `starwars` dataset from the tidyverse package:

Example: Define a function that takes a character's name as an argument and returns their species.

```{r eval=FALSE, include=TRUE}
get_species <- function(name) {
  species <- starwars %>% filter(name == !!name) %>% select(species) %>% pull()
  return(species)
}

get_species("Luke Skywalker")
```

The `!!` before the name argument is a syntax called "bang bang" operator, which tells R to evaluate the argument immediately instead of delaying it. This is because the argument name is used within the filter function, which requires immediate evaluation of the argument.

1\. Define a function that takes in a character's name and returns a dataframe containing the name, birth year, and species of that character.


2\. Define a function that takes in a character's name and returns their height in meters.


3\. Define a function that takes in a planet's name and returns the number of characters whose homeworld is this planet.


4\. Define a function that takes in a planet name and returns a dataframe containing the names and heights of all characters from that planet, sorted by height in descending order.


5\. Define a function that takes a character's name as an argument and returns the average height of all characters from the same species as that character.


6\. Define a function that takes in a character's name and a planet name, and returns a dataframe containing the name and gender of all characters from that planet who share the same gender as the input character.