---
title: "Exercise 2 - Introductory Exercises"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Welcome to the Star Wars Universe!

## Recap: Last Week's `Star Wars`Homework

1\. How many droids are there?

```{r eval=FALSE, include=TRUE}
starwars %>%
   filter(species == 'Droid') %>%
   summarise(n())
```

2\. What is the home world of Han Solo?

```{r eval=FALSE, include=TRUE}
starwars %>%
   select(name, homeworld) %>%
   filter(name == 'Han Solo')
```

3\. How many characters are there per species? Sort by descending count.

```{r eval=FALSE, include=TRUE}
starwars %>%
    group_by(species) %>%
    summarise(count = n()) %>%
    arrange(desc(count))
```

4\. Change the height from `cm` to `m`.

```{r eval=FALSE, include=TRUE}
starwars %>%
   mutate(height = height / 100)
```

5\. Filter out all characters that have missing values (´NA`) for their mass. How many are left?

```{r eval=FALSE, include=TRUE}
starwars %>%
   select(name, mass) %>%
   na.omit()
```

## Further `Star Wars` Tasks - Breakout Rooms

1\. Find all characters with yellow eyes.
```R
> starwars %>%
+     select(name, eye_color) %>%
+     filter(eye_color == 'yellow')
# A tibble: 11 x 2
   name              eye_color
   <chr>             <chr>
 1 C-3PO             yellow
 2 Darth Vader       yellow
 3 Palpatine         yellow
 4 Watto             yellow
 5 Darth Maul        yellow
 6 Dud Bolt          yellow
 7 Ki-Adi-Mundi      yellow
 8 Yarael Poof       yellow
 9 Poggle the Lesser yellow
10 Zam Wesell        yellow
11 Dexter Jettster   yellow
```
2\. Remove all Gungans. How many characters are left?
```R
> starwars %>%
+     filter(is.na(species)|species != 'Gungan')
# A tibble: 84 x 14
```
3\. What is the average mass of all droids?
```R
> starwars %>%
+     select(name, species, mass) %>%
+     filter(species == 'Droid') %>%
+     na.omit() %>%
+     summarise(mean(mass))
# A tibble: 1 x 1
  `mean(mass)`
         <dbl>
1         69.8
```
4\. Calculate the BMI for all humans (\`mass / ((height / 100) ^ 2)\`)
```R
> starwars %>%
+     select(name, mass, height, species) %>%
+     filter(species == 'Human') %>%
+     filter(!is.na(mass)) %>%
+     filter(!is.na(height)) %>%
+     mutate(bmi = (mass / ((height / 100) ^ 2)))
# A tibble: 22 x 5
   name                mass height species   bmi
   <chr>              <dbl>  <int> <chr>   <dbl>
 1 Luke Skywalker        77    172 Human    26.0
 2 Darth Vader          136    202 Human    33.3
 3 Leia Organa           49    150 Human    21.8
 4 Owen Lars            120    178 Human    37.9
 5 Beru Whitesun lars    75    165 Human    27.5
 6 Biggs Darklighter     84    183 Human    25.1
 7 Obi-Wan Kenobi        77    182 Human    23.2
 8 Anakin Skywalker      84    188 Human    23.8
 9 Han Solo              80    180 Human    24.7
10 Wedge Antilles        77    170 Human    26.6
# … with 12 more rows
```
5\. Which character has the longest name?
```R
> starwars %>%
+     select(name) %>%
+     arrange(desc(str_length(name))) %>%
+     filter(row_number()==1)
# A tibble: 1 x 1
   name
   <chr>
 1 Jabba Desilijic Tiure

```
6\. What is the earliest birth year for each species (\`birth_year\` is measured in BBY = Before Battle of Yavin, so high values = earlier)
```R
> starwars %>%
+     filter(!is.na(birth_year)) %>%
+     filter(!is.na(species)) %>%
+     group_by(species) %>%
+     arrange(birth_year) %>%
+     summarise(max(birth_year))
# A tibble: 15 x 2
   species        `max(birth_year)`
   <chr>                      <dbl>
 1 Cerean                        92
 2 Droid                        112
 3 Ewok                           8
 4 Gungan                        52
 5 Human                        102
 6 Hutt                         600
 7 Kel Dor                       22
 8 Mirialan                      58
 9 Mon Calamari                  41
10 Rodian                        44
11 Trandoshan                    53
12 Twi'lek                       48
13 Wookiee                      200
14 Yoda's species               896
15 Zabrak                        54
```
7\. What are the most populated planets?
```R
> starwars %>%
+     group_by(homeworld) %>%
+     summarise(n = n()) %>%
+     arrange(desc(n))
# A tibble: 49 x 2
   homeworld     n
   <chr>     <int>
 1 Naboo        11
 2 Tatooine     10
 3 NA           10
 4 Alderaan      3
 5 Coruscant     3
 6 Kamino        3
 7 Corellia      2
 8 Kashyyyk      2
 9 Mirial        2
10 Ryloth        2
# … with 39 more rows
```
8\. What is the average height of all female humans?
```R
> starwars %>%
+     select(name, height, gender, species) %>%
+     filter(species == 'Human', gender == 'feminine') %>%
+     na.omit() %>%
+     summarise(mean(height))
# A tibble: 1 x 1
  `mean(height)`
           <dbl>
1           160.
```
9\. Which planet has the most droids? 
```R
> starwars %>%
+     filter(species == 'Droid') %>%
+     group_by(homeworld) %>%
+     summarise(n = n()) %>%
+     arrange(desc(n))
# A tibble: 3 x 2
  homeworld     n
  <chr>     <int>
1 NA            3
2 Tatooine      2
3 Naboo         1
```
10\. Which is the most prevalent eye color on each planet?
```R
> starwars %>%
+       group_by(homeworld, eye_color) %>% 
+       mutate(rank = row_number()) %>% 
+       group_by(homeworld) %>% 
+       slice(which.max(rank)) %>% 
+       summarise(homeworld, eye_color, rank)
```
11\. How many unique eye colors are there?
```R
> starwars %>%
+       summarise(eye_color) %>%
+       distinct(eye_color)
# A tibble: 15 x 1
   eye_color
   <chr>
 1 blue
 2 yellow
 3 red
 4 brown
 5 blue-gray
 6 black
 7 orange
 8 hazel
 9 pink
10 unknown
11 red, blue
12 gold
13 green, yellow
14 white
15 dark
```